---
title: "Check Results"
author: "Carmen"
date: "March 27, 2018"
output: html_document
---


```{r}
library(tidyverse)
library(raster)
library(sp)
```

# Set county
```{r}
county <- "Amador"
```

# Load that county's results

## Yearly
```{r}
setwd("~/drought_tree_carbon/drought_tree_carbon/code")
years <- c("2013","2014","2015","2016","2017")
for(i in 1:length(years)){
  load(paste("../Results/Results_Table_",  years[i], county,".Rdata", sep = ""))
  assign(paste( "df", years[i],sep = ""), df)
  remove(df)
  load(paste("../Results/Results_Spatial_", years[i], county, ".Rdata", sep = ""))
  assign(paste("spdf", years[i], sep = ""), spdf)
  remove(spdf)
}
```

## Overall
```{r}
setwd("~/drought_tree_carbon/drought_tree_carbon/results/")
ag <- read.csv(paste("tables_aggregated/", county, "_aggregated.csv", sep = ""))
load(paste("Results_Table_", county, ".Rdata", sep = ""))
load(paste("Results_Spatial_", county, ".Rdata", sep = ""))
```

# Look at data table
```{r}
head(df)
head(df2013)
```

# Check that spatial matches table
```{r}
sum(na.omit(df2013$D_BM_kg))==sum(na.omit(spdf2013@data$D_BM_kg))
sum(na.omit(df2014$D_BM_kg))==sum(na.omit(spdf2014@data$D_BM_kg))
sum(na.omit(df2015$D_BM_kg))==sum(na.omit(spdf2015@data$D_BM_kg))
sum(na.omit(df2016$D_BM_kg))==sum(na.omit(spdf2016@data$D_BM_kg))
sum(na.omit(df2017$D_BM_kg))==sum(na.omit(spdf2017@data$D_BM_kg))
```

# Check that yearly results somewhat match overall results
```{r}
sum_years <- sum(na.omit(df2013$D_BM_kg)) + sum(na.omit(df2014$D_BM_kg)) + sum(na.omit(df2015$D_BM_kg)) + sum(na.omit(spdf2016@data$D_BM_kg)) + sum(na.omit(df2017$D_BM_kg))
sum_years

sum(na.omit(df$D_BM_kg))/sum_years


```

```{r}

```


# Check that aggregated results match non-aggregated results

## Change columns to numeric
```{r}
head(ag)
ag[3:6] <- lapply(ag[,3:6],as.character)
ag[3:6] <- lapply(ag[,3:6],as.numeric)
head(ag)
```

## Sum aggregated results
```{r}
sumag <- ag %>% 
  summarise(liveBM = sum(na.omit(BM_live_2012_kg)), deadBM=sum(na.omit(D_BM_kg)), deadT = sum(na.omit(NO_TREES_DEAD)), liveT = sum(na.omit(NO_TREES_PX)))
sumag            
```

```{r}
sumag$deadBM/sumag$liveBM
sumag$deadT/sumag$liveT
```

## Sum live biomass and live number of trees across the different data sets
```{r}
sum(spdf$BM_live_2012_kg)
sum(df$BM_live_2012_kg)
sum(na.omit(ag$BM_live_2012_kg))
```

## The below should equal 1
```{r}
sum(df$BM_live_2012_kg)/sum(na.omit(ag$BM_live_2012_kg))
```

# Check results table

## Check for repeated rows - there should be none
```{r}
summary(as.numeric(df$pixel_key))
repeats <- df %>% group_by(x,y) %>% filter(n()>1)
nrow(repeats) == 0
```

## Check for rows with dead biomass data but no live biomass data -- there should be none
```{r}
huh <- df %>% filter(is.na(BM_live_2012_kg) & !is.na(D_BM_kg))
nrow(huh) == 0
```

## Check for greater than 100% mortality
```{r}
summary(df$Percent_Mortality_Biomass)
summary(df$Percent_Mortality_Count)
max(na.omit(df$Percent_Mortality_Biomass) > 100)==FALSE
max(na.omit(df$Percent_Mortality_Count) > 100)==FALSE
```

# Check for rows with no pre-mortality biomass
```{r}
df2014 %>% filter(NO_TREES_PX == 0) %>% summarise(n())
df %>% filter(NO_TREES_PX == 0) %>% summarise(n())
```

