---
title: "map_southsierra"
author: "Carmen"
date: "January 23, 2018"
output: html_document
---
  
  This is based on the code from map_new_unit in the drought_tree_carbon github repository. 

Load packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(dplyr)
library(RColorBrewer)
library(ggsn)
library(rgeos)
library(ggmap)
```

# PREP RESULTS

## Load
```{r}
setwd("~/drought_tree_carbon/sierra_regions/results/NE_Sierra/")
load("Results_Table_subregion_NE_Sierra.Rdata")
load("Results_Spatial_subregion_NE_Sierra.Rdata")
```

## Split into smaller data frames
```{r}
splits <- split(seq(nrow(df)), c(1:6))
for(i in 1:6){
  dfi <- df[splits[[i]],]
  assign(paste("df",i, sep = ""), dfi)
}
```

Check
```{r}
nrow(df1)+nrow(df2)+nrow(df3)+nrow(df4)+nrow(df5)+nrow(df6) == nrow(df)
```

# PREP REGION BOUNDARY

## Load 
```{r}
setwd("~/drought_tree_carbon/sierra_regions/data/sierra_regions")
region <- readOGR(dsn = "subregion_NE_Sierra", layer = "subregion_NE_Sierra")
region <- spTransform(region, crs(spdf))
plot(region)
```

## Convert format
```{r}
region@data$id = rownames(region@data)
region.points = fortify(region, region="id")
region.bound = full_join(region.points, region@data, by="id")
region.cent <- as.data.frame(coordinates(region))
```

# Set formatting of map
```{r}
cols <- c('#a1d99b','#feb24c','#fd8d3c','#fc4e2a','#e31a1c','#b10026') # define colors
scale_res <- round((extent(region)[2]-extent(region)[1])/2000, digits =0)
```

# Map - do not try to plot this in R! It's too big
```{r}

map_figure <- ggplot()+
  geom_tile(data= df1,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  geom_tile(data= df2,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  geom_tile(data= df3,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  geom_tile(data= df4,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  geom_tile(data= df5,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  geom_tile(data= df6,aes(x=x,y=y,fill = Percent_Mortality_Biomass, color=Percent_Mortality_Biomass))+
  
  scale_colour_gradientn(colours = cols,
                         breaks=c(0,.05,.25,.5,.75,1),
                         labels=c("","5%","25%","50%","75%","100%"),
                         limits=c(0,1),
                         na.value="white")+
  scale_fill_gradientn(colours = cols,
                       limits=c(0,1),
                       breaks=c(0,.05,.25,.5,.75,1),
                       labels=c("","5%","25%","50%","75%","100%"),
                       na.value="white")+
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(), axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background=element_blank(),
        panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        plot.background=element_blank(),
        legend.title=element_blank(),
        plot.margin=unit(c(.5,.5,.5,.5), "cm"),
        plot.title = element_text(size = 20), 
        legend.position = c(.85, .95),  
        panel.border = element_rect(colour = "black", fill=NA, size=1))+
  labs(title=paste("Percent loss of live adult tree aboveground biomass, \n2012-2016, North Sierra"))+
  geom_path(data=region.bound, aes(x=long,y=lat,group=group),color="black")+
  north(data = region.bound, location = "topleft", scale=.05,symbol=12)+
  scalebar(data=region.bound, dist = scale_res)+
  coord_fixed(ratio = 1)
```


# Save
```{r}
setwd("~/drought_tree_carbon/sierra_regions/results/NE_Sierra/")
jpeg("NE_sierra_map.jpeg", width = 1000, height = 1400, quality = 200)
map_figure
dev.off()
```

# Convert to lat/long
```{r}
spdf_latlong <- spTransform(spdf, CRS("+proj=longlat +datum=WGS84"))
crs(spdf_latlong)
head(spdf_latlong@data)

```

# Make a data frame
```{r}
spdf_latlong_df <- data.frame(slot(spdf_latlong, "coords"), spdf_latlong@data$Percent_Mortality_Biomass)
head(spdf_latlong_df)
```

# Set up base map
```{r}
mapImageData <- get_map(location = c(lon = -120.75,
  lat = 40.974),
  color = "color", # or bw
  source = "google",
  maptype = "satellite",
  zoom = 7)
ggmap(mapImageData)
```



## Split into smaller data frames
```{r}
splits <- split(seq(nrow(spdf_latlong_df)), c(1:20))
for(i in 1:20){
  spdf_latlong_dfi <- spdf_latlong_df[splits[[i]],]
  assign(paste("spdf_latlong_df",i, sep = ""), spdf_latlong_dfi)
}
```


```{r}
map_image <- ggmap(mapImageData)+
  geom_tile(data= spdf_latlong_df1,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
 # geom_tile(data= spdf_latlong_df2,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
  # geom_tile(data= spdf_latlong_df3,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
  # geom_tile(data= spdf_latlong_df4,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
  # geom_tile(data= spdf_latlong_df5,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
  # geom_tile(data= spdf_latlong_df6,aes(x=x,y=y,fill = spdf_latlong.data.Percent_Mortality_Biomass, color=spdf_latlong.data.Percent_Mortality_Biomass))+
  
  scale_colour_gradientn(colours = cols,
                         breaks=c(0,.05,.25,.5,.75,1),
                         labels=c("","5%","25%","50%","75%","100%"),
                         limits=c(0,1),
                         na.value="white")+
  scale_fill_gradientn(colours = cols,
                       limits=c(0,1),
                       breaks=c(0,.05,.25,.5,.75,1),
                       labels=c("","5%","25%","50%","75%","100%"),
                       na.value="white")+
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(), axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background=element_blank(),
        panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        plot.background=element_blank(),
        legend.title=element_blank(),
        plot.margin=unit(c(.5,.5,.5,.5), "cm"),
        plot.title = element_text(size = 20), 
        legend.position = c(.85, .95),  
        panel.border = element_rect(colour = "black", fill=NA, size=1))+
  labs(title=paste("Percent loss of live adult tree aboveground biomass, \n2012-2016, North Sierra"))
  # north(data = region.bound, location = "topleft", scale=.05,symbol=12)+
  # scalebar(data=region.bound, dist = scale_res)+
  #coord_fixed(ratio = 1)
```


# Save map image
```{r}
setwd("~/drought_tree_carbon/sierra_regions/results/NE_Sierra/")
jpeg("NE_sierra_map_image.jpeg")
map_image
dev.off()
```

